Resource Buying Games

### 2017-03-01 paper.tex
introduced congestion model

\documentclass{scrartcl}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usepackage{framed}
\usepackage{todo}
\usepackage[framed]{ntheorem}

@@

@@

having a vector space by giving instead of linear independent sets the bases of
the ground-set.

@@

>>>>

\documentclass{scrartcl}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usepackage{framed}
\usepackage{todo}
\usepackage{amsmath}
\usepackage[framed]{ntheorem}

@@

\section{Congestion Model}
In this section we want to introduce a structure to model resources and demands
of actors on resources. Therefore, we consider a set of players $N$ and a set
of resources $E$. Every player has a personal aim which can be achieved by
different resources. This is modelled for a player $i\in N$ as family
$\mathcal{S}_{i}$ of sets $S_{i}\subseteq E$ of resources. Additionally, we
want to account for different demands of players on resources by fixing a
demand for every player $i$ as $d_{i}\in\mathbb{N}$. Finally, the cost of a
resource depends on the load the players put onto the resource modelled as
individual cost functions $c_{e}:\mathbb{N}\rightarrow \mathbb{N}$ for every
resource $e\in E$. As an example consider different actors that build a shared
network infrastructure. The connections in the network are resources, the
actors are the players which have individual spots they want to connect.
Different actors might need different bandwidth for connections, i.e. their
demands, and the cost for using connections depends on the used bandwidth.
Accordingly we obtain a congestion model
\begin{equation*}
  \mathcal{M} = \tupel{N, E, \mathcal{S} = \times_{i\in N}\mathcal{S}_{i},
  (d_{i})_{i\in N}, (c_{e})_{e\in E}}
\end{equation*}
for which we introduce some additional definitions:
\begin{itemize}
  \item for a profile $S\in\mathcal{S}$ we define
    the demand on resource $e$ for $S$ as
    $\ell(S) = \sum_{i\in N:e\in S_{i}}d_{i}$
  \item we lift $c_{e}$ to the set $\mathcal{S}$ by setting
    $c_{e}(S) = c_{e}(\ell_{e}(S))$ for $S\in\mathcal{S}$
\end{itemize}
\todo{complete list of auxilary definitions}

@@

bases of a vector space by giving the inclusion-wise maximal linear independent
sets (in analogy also called bases).

@@

\section{Unweighted Matroid Games}
